---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# mockr

The goal of mockr is to provide a drop-in replacement for `testthat::with_mock()`
which will be deprecated in the next version of `testthat`. The only exported
function, `with_mock()`, is modeled closely after the original implementation,
but now only allows mocking functions in the package under test, which is
good practice anyway. In contrast to the original implementation, no fiddling
with R's internals is needed.

- If you need to mock an external function, write a wrapper.
- The original implementation allowed modifying the behavior of other packages'
  functions. this is discouraged (and not possible with this implementation).

## Example

```{r load, echo=FALSE}
devtools::load_all()
```

```{r example, error = TRUE}
some_func <- function() stop("oops")
some_other_func <- function() some_func()

# Calling this function gives an error
some_other_func()

tester_func <- function() {
  # Here, we override the function that raises the error
  with_mock(
    some_func = function() 42,
    some_other_func()
  )
}

# No error raised
tester_func()

# Mocking doesn't override functions in the same environment by design
with_mock(some_func = function() 6 * 7, some_other_func())
```

## Installation

Install from GitHub via

```r
devtools::install_github("krlmlr/mockr")
```
