---
title: "Mocking with mockr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mockr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The mockr package helps testing code that relies on functions that are slow, have unintended side effects or access resources that may not be available when testing.
It allows replacing such functions with deterministic [*mock functions*](https://en.wikipedia.org/wiki/Mock_object).
This article gives an overview and introduces a few techniques.

```{r setup}
library(mockr)
```

## General idea

Let's assume a function `access_resource()` that accesses some resource.
This works in normal circumstances, but not during tests.
A function `work_with_resource()` works with that resource.
How can we test `work_with_resource()` without adding too much logic to the implementation?

```{r fun-def}
access_resource <- function() {
  message("Trying to access resource...")
  # For some reason we can't access the resource in our tests.
  stop("Can't access resource now.")
}

work_with_resource <- function() {
  resource <- access_resource()
  message("Fetched resource: ", resource)
  invisible(resource)
}
```

In our example, calling the worker function gives an error:

```{r example-error, error = TRUE}
work_with_resource()
```

We can use `local_mock()` to temporarily replace the implementation of `access_resource()` with one that doesn't throw an error:

```{r example-remedy}
access_resource_for_test <- function() {
  # We return a value that's good enough for testing
  # and can be computed quickly:
  42
}

local({
  # Here, we override the function that raises the error
  local_mock(access_resource = access_resource_for_test)

  work_with_resource()
})
```

The use of `local()` here is required for technical reasons.
This package is most useful in conjunction with testthat, the remainder of this article will focus on that use case.


## Create demo package

## Slow function with side effect

## Adding test with mock

## Run all tests in package

## Run individual tests

## Write wrapper functions

## Mock S3 methods
