---
title: "Mocking with mockr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mocking with mockr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

set.seed(20201218)
```

The mockr package helps testing code that relies on functions that are slow, have unintended side effects or access resources that may not be available when testing.
It allows replacing such functions with deterministic [*mock functions*](https://en.wikipedia.org/wiki/Mock_object).
This article gives an overview and introduces a few techniques.

```{r setup}
library(mockr)
```

## General idea

Let's assume a function `access_resource()` that accesses some resource.
This works in normal circumstances, but not during tests.
A function `work_with_resource()` works with that resource.
How can we test `work_with_resource()` without adding too much logic to the implementation?

```{r fun-def}
access_resource <- function() {
  message("Trying to access resource...")
  # For some reason we can't access the resource in our tests.
  stop("Can't access resource now.")
}

work_with_resource <- function() {
  resource <- access_resource()
  message("Fetched resource: ", resource)
  invisible(resource)
}
```

In our example, calling the worker function gives an error:

```{r example-error, error = TRUE}
work_with_resource()
```

We can use `local_mock()` to temporarily replace the implementation of `access_resource()` with one that doesn't throw an error:

```{r example-remedy}
access_resource_for_test <- function() {
  # We return a value that's good enough for testing
  # and can be computed quickly:
  42
}

local({
  # Here, we override the function that raises the error
  local_mock(access_resource = access_resource_for_test)

  work_with_resource()
})
```

The use of `local()` here is required for technical reasons.
This package is most useful in conjunction with testthat, the remainder of this article will focus on that use case.


## Create demo package

We create a package called {mocktest} for demonstration.
For this demo, the package is created in a temporary directory.
A real project will live somewhere in your home directory.
The `usethis::create_package()` function sets up a package project ready for development.
The output shows the details of the package created.

```{r create-package}
pkg <- usethis::create_package(file.path(tempdir(), "mocktest"))
```

In an interactive RStudio session, a new window opens.
Users of other environments would change the working directory manually.
For this demo, we manually set the active project.

```{r set-focus, include = FALSE}
wd <- getwd()

knitr::knit_hooks$set(
  pkg = function(before, options, envir) {
    if (before) {
      wd <<- setwd(pkg)
    } else {
      setwd(wd)
    }

    invisible()
  }
)

knitr::opts_chunk$set(pkg = TRUE)
```

```{r pkg-location}
usethis::proj_set()
```

The infrastructure files and directories that comprise a minimal R package are created:

```{r dir-tree}
fs::dir_tree()
```

## Import function

We copy the functions from the previous example (under different names) into the package.
Normally we would use a text editor:

```{bash import}
cat > R/resource.R <<"EOF"
access_resource_pkg <- function() {
  message("Trying to access resource...")
  # For some reason we can't access the resource in our tests.
  stop("Can't access resource now.")
}

work_with_resource_pkg <- function() {
  resource <- access_resource_pkg()
  message("Fetched resource: ", resource)
  invisible(resource)
}
EOF
```

Loading the package and calling the function gives the error we have seen before:

```{r run-pkg, error = TRUE}
pkgload::load_all()
work_with_resource_pkg()
```

## Adding test with mock

We create a test that tests `work_with_resource_pkg()`, mocking `access_resource_pkg()`.
We need to prefix with the package name, because testthat provides its own `testthat::local_mock()` which is now deprecated.

```{r test}
usethis::use_testthat()
```

```{bash create-test}
cat > tests/testthat/test-resource.R <<"EOF"
test_that("Can work with resource", {
  mockr::local_mock(access_resource_pkg = function() {
    42
  })

  expect_message(expect_equal(work_with_resource_pkg(), 42))
})
EOF
```

The test succeeds:

```{r error = TRUE}
testthat::test_local(reporter = "location")
```


## Run individual tests



## Write wrapper functions

## Mock S3 methods

## The development phase
